Functional Analysis of CGM Data

### 2022-12-02 StatNet/cgm_fda.qmd
FPCA on first day only

ydf = do.call(rbind,ys[keep])

@@

- The goals of FDA are essentially the same as other areas of statistics:
  1. Represent data to aid in analysis and to highlight characteristics
  2. Study patterns and sources of variation
  3. Explain variation in an outcome using independent variables

- Common uses of FDA:
  - Growth data
  - Imaging data 
  - Wearable device data
  - Accelerometry (physical activity) 
  - Heart rate
  - **Continuous glucose monitoring** (CGM)

@@

```{r results='asis'}
demo = fda_df %>%
  select(Subject.ID:Average.BMI.Z.score) %>% 
  group_by(Subject.ID) %>% 
  summarise(Age = Age[1],Gender = Gender[1],Race = Race.Ethnicity[1],
            Insulin = CF.Insulin.Use[1],`BMI Z Score`= Average.BMI.Z.score[1],
            `Days of Data` = n(),Group = Combined.Group.Category[1])
t1 = 
  tableby(Group~Age+Gender+Race+Insulin+`BMI Z Score`+`Days of Data`,
             data = demo)
summary(t1)
```

@@

>>>>

sleep = sleep %>% unite("id_day",Subject.ID,Day,remove = F)
names(ys) = sleep$id_day
# Limit to first day with no missing
sleep = sleep[keep,]
  group_by(Subject.ID) %>%
  filter(row_number()==1)
ys = ys[sleep$id_day]
# Combine
ydf = do.call(rbind,ys)

@@

-   The goals of FDA are essentially the same as other areas of statistics:
    1.  Represent data to aid in analysis and to highlight characteristics
    2.  Study patterns and sources of variation
    3.  Explain variation in an outcome using independent variables
-   Common uses of FDA:
    -   Growth data
    -   Imaging data
    -   Wearable device data
    -   Accelerometry (physical activity)
    -   Heart rate
    -   **Continuous glucose monitoring** (CGM)

@@

```{r results='asis'}
sleep = sleep %>%
  select(Subject.ID:Average.BMI.Z.score) %>% 
  rename(Age = Age,Gender = Gender,Race = Race.Ethnicity,
            Insulin = CF.Insulin.Use,`BMI Z Score`= Average.BMI.Z.score,
            Group = Combined.Group.Category)
t1 = tableby(Group~Age+Gender+Race+Insulin+`BMI Z Score`,data = sleep)
summary(t1)
```

@@

This plot includes all days of data, but the following analyses is only the first day due to computing limitations.
